Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-06 cmsb22.tex
Answer questions

@@

\sylvain{I might add a small figure for the example later\dots}

@@

\sylvain{It seems that the RA\_apoptosis model is only 180 nodes, where does the n = 431 come from?}

@@

\sylvain{the \texttt{dom-pref} thing is deprecated since 2014 but still used in PyBoolNet, I think we might give the more modern version I used in the Python script, but we'll see}
% \subsection{Benchmark vs.\ implicant-based methods}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Drawing
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{tikz}
\usepackage{amsfonts}

\usetikzlibrary{positioning,automata} % drawing automa
\usetikzlibrary{calc,fit,tikzmark}

% for captions in figures
\usepackage{subcaption}

@@

\begin{figure}[!ht]
\centering
\begin{subfigure}[b]{0.5\textwidth}
\centering
\begin{tikzpicture}[node distance=1cm and 1cm, every node/.style={scale=1.0}]
   \node[circle,draw] (0) [] {00};
   \node[circle,draw] (1) [above=of 0] {01};
   \node[circle,draw] (2) [right=of 0] {10};
   \node[circle,draw] (3) [above=of 2] {11};

   \draw[->] (0) edge [bend left] (1);
   \draw[->] (0) edge [bend right] (2);

   \draw[->] (1) edge [bend left] (0);
   \draw[->] (1) edge [loop right] (1);

   \draw[->] (2) edge [bend right] (0);
   \draw[->] (2) edge [loop right] (2);

   \draw[->] (3) edge [loop right] (3);
\end{tikzpicture}
\caption{}
\end{subfigure}%
\begin{subfigure}[b]{0.5\textwidth}
\centering
\caption{}
\end{subfigure}%
\caption{(a) STG under the fully asynchronous update of the Boolean model. (b) Petri net encoding of the Boolean model.}
\label{fig:stg_and_PN}
\end{figure}

\sylvain{I might add a small figure for the example later\dots}
\vangiang{In this small figure, we can show the STG under the fully asynchronous update and the Petri net encoding of the Boolean model.}

@@

\sylvain{It seems that the RA\_apoptosis model is only 180 nodes, where does the n = 431 come from?}
\vangiang{n = 431 comes from Table 1 of~\cite{aghamiri2020automated}. I have checked this model. It has only 180 nodes. I will check others models come from~\cite{aghamiri2020automated}.}

@@

\sylvain{the \texttt{dom-pref} thing is deprecated since 2014 but still used in PyBoolNet, I think we might give the more modern version I used in the Python script, but we'll see}
\vangiang{I also found that you did not use the \texttt{dom-pref} thing in the Python script. I think we should use the same configuration as that used in PyBoolNet.}

% \subsection{Benchmark vs.\ implicant-based methods}
